---
title: "simulating data"
description: |
  Attempts to simulate data for a later post.
author: Peter Yao
date: 08-04-2021
output:
  distill::distill_article:
    self_contained: false
categories:
  - work-in-progress
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I want to describe an old project that required some interesting data analysis but first I need to find a way to create some artificial data.
I basically need data from a step function, with some noise added.
Each step has to have some "measurement" points in the middle.
At first I tried to make my own step function in a naïve way, as shown below.
I did not realise literally until I started writing this post and wrote a function called `step_func` that R has a built-in function `stats::stepfun`, which I need to learn more about.

```{r imports, echo=FALSE}
library("ggplot2")
```


```{r step}
step_func <- function(n = 100L, m = 10L) {
  dat <- sapply(1:n, function(x) rep(x, m))
  
  data.frame(
    x = 0:((n * m ) - 1), 
    y = as.vector(dat)
  )
}

step_dat <- step_func(n = 20, m = 4)
ggplot2::ggplot(step_dat, ggplot2::aes(x = x, y = y)) +
  ggplot2::geom_point()
```

This is fine but I also need occasionally lower steps.
It turned out one way to do this is to essentially simulate the underlying process that I was studying, by using a cumulative sum, with the step height sometimes decreased according to a probability in `rbinom`.
I also add noise in the function below, and drop some of the "measurement" points randomly.

```{r sim}
set.seed(100)

make_data <- function(n = 100L,
                      m = 10L,
                      p = 0.15,
                      rmin = 0.2,
                      rmax = 0.8,
                      sd_x = 0.02,
                      sd_y = 0.02,
                      del_frac = 0.05) {

  sim <- data.frame(
    x = seq(m, n * m, by = m),
    y = 1 - rbinom(n, 1, p) * runif(n, min = rmin, max = rmax)
    )
  
  meas <- data.frame(
    x = 0:(n * m),
    noise_x = rnorm((n * m) + 1, mean = 0, sd = sd_x),
    noise_y = rnorm((n * m) + 1, mean = 0, sd = sd_y)
  )
  
  sim_noisy <- merge(sim, meas, all = TRUE)
  sim_noisy$y_noisy <- rowSums(sim_noisy[, c("y", "noise_y")], na.rm = TRUE)
  sim_noisy$x_noisy <- rowSums(sim_noisy[, c("x", "noise_x")], na.rm = TRUE)
  sim_noisy$cumul_noisy <- cumsum(sim_noisy$y_noisy)

  del_nrows = as.integer(n * m * del_frac)
  del_rows <- sample(n * m, del_nrows, replace = FALSE)
  
  sim_noisy[-del_rows, c("x_noisy", "cumul_noisy")]
}

sim_dat <- make_data(n = 20, m = 4)

ggplot2::ggplot(sim_dat, ggplot2::aes(x = x_noisy, y = cumul_noisy)) +
  ggplot2::geom_point()
```
