---
title: "autoportrait"
description: Documenting how this blog was set up
author: Peter Yao
date: 07-31-2021
output:
  distill::distill_article:
    self_contained: false
categories:
  - distill
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

This blog was set up following the instructions from [Alison Hill](https://distillery.rbind.io/posts/2021-03-16-postcards-distill/).
To make the rest of the site match the [About Me](https://peterjyao.github.io/vitae/index.html) page better (created with the [postcards](https://github.com/seankross/postcards) package), I added a bit to the site `styles.css`, which I expect I will play with more in the future.

```{css, echo=TRUE}
@import url("https://fonts.googleapis.com/css2?family=Roboto+Slab&display=swap");

h1, h2, h3, h4, h5, h6 {
  font-family: "Roboto Slab";
}

body {
  font-family: "Roboto Slab";
  background-color: #f5e9dd;
}
```

At the moment there is a slight difference in how the navbar looks on the pages.
Hopefully I can figure out how to fix that at some point.

I wanted to try to use the same data source I used for [my CV](https://peterjyao.github.io/vitae/assets/cv.pdf), which I partially made using the [vitae](https://github.com/mitchelloharawild/vitae/) package--I say partially, because I ended up fine tuning it directly in the LaTeX file.
It's a bit hacky but works.
Below is for the "Experience" section.

```{r demo, echo=TRUE, eval=FALSE}
library("glue")

data_source_root <- "https://raw.githubusercontent.com/peterjyao/cv/main/data"

experience <- read.csv(url(glue("{data_source_root}/experience.csv")))

# fix the date formatting
experience$dates <- gsub("\'", "20", experience$dates)
experience$dates <- gsub("-", " - ", experience$dates)

experience$description_formatted <- glue(
    .envir = experience,
    "**{role}**&nbsp;&nbsp;|&nbsp;&nbsp;{dates}",
    "*{org}*&nbsp;&nbsp;|&nbsp;&nbsp;{place}",
    "{description}",
    .sep = "<br>"
  )

cat(paste(experience$description_formatted, collapse = "<br><br>"))
```

I used similar code for the "Education" and "Languages" section, so I should probably make a function out of it.